---
title: "Homework 1: ggplot2"
author: "Valter Aro"
date: "2019-03-08"
output: github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
mpg
```

By using *mpg* dataset:

1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

- Color
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))
#Color can be used for both continous variables and catergorical ones. With continous variables the color will be in a gradient from one extreme to the other.
```

- Size
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, size = cty))
#Size is not suitable for categorical variables, but is decent for continous variables.

```

- Shape
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, shape = trans))
#Shape can not be used for continous variables
```


2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ))
#Multiple aesthetics can be used for the same variable, but in most cases it does provide a better way for understanding the information.
```


3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, stroke = cty, shape = trans))
#Stroke is the size of the marker in the plot. For continous values it will be the number. It can not be used for categorical variables.
#For shapes that have a border (like 21), you can colour the inside and for shapes that have a border (like 21), you can colour the inside and
# outside separately. Use the stroke aesthetic to modify the width of the border
#For shapes 20-24 stroke changes the width of the border.
```

4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
#When you map an aesthetic to a logic test it gives a TRUE or FALSE value in a given format.
```
